---
title: "Relationship between early life experience and WTP for conservation "
author: "Liqing"
date: "9/23/2018"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Surey location choice - Net migration rate
data:https://netmigration.wisc.edu/

```{r library}
library(dplyr)
library(data.table)

```


1980-2000 all counties
```{r 1980-2000 all counties}
nm<-read.csv("/Users/liqingli/Dropbox/WTP for urban parks/Data/WTP/location choice/1980-2000_all/netmigration_1538669685697.csv")

nm_IL<-nm%>%
  filter(stname=="Illinois")
```




For Metro counties only:
```{r 1980-2000s metro}
nm_metro<-read.csv("/Users/liqingli/Dropbox/WTP for urban parks/Data/WTP/location choice/1980-2000_metro/netmigration_1537759824444.csv")

```
State IL with high and low net migration rates
```{r}
#d[order(d$V4,decreasing=T)[1:5],]
nm_IL_metro<-nm_metro%>%
  filter(stname=="Illinois")
nm_IL_metro_dt<-as.data.table(nm_IL_metro)
# Top 5
IL_2000_t5=nm_IL_metro_dt[order(total_2000,decreasing = T)[1:5],][,c("name","total_2000")]
IL_2000_t5

IL_1990_t5=nm_IL_metro_dt[order(total_1990,decreasing = T)[1:5],][,c("name","total_1990")]
IL_1990_t5

IL_1980_t5=nm_IL_metro_dt[order(total_1980,decreasing = T)[1:5],][,c("name","total_1980")]
IL_1980_t5

#Last 5
nm_IL_metro_dt= nm_IL_metro_dt[,total_2000.abs:=abs(total_2000)]
nm_IL_metro_dt= nm_IL_metro_dt[,total_1990.abs:=abs(total_1990)]
nm_IL_metro_dt= nm_IL_metro_dt[,total_1980.abs:=abs(total_1980)]

IL_2000_b5=nm_IL_metro_dt[order(total_2000.abs)[1:5],][,c("name","total_2000.abs")]
IL_2000_b5

IL_1990_b5=nm_IL_metro_dt[order(total_1990.abs)[1:5],][,c("name","total_1990.abs")]
IL_1990_b5

IL_1980_b5=nm_IL_metro_dt[order(total_1980.abs)[1:5],][,c("name","total_1980.abs")]
IL_1980_b5
```

State Iowa with high and low net migration rates
```{r}

nm_IA_metro<-nm_metro%>%
  filter(stname=="Iowa")
nm_IA_metro_dt<-as.data.table(nm_IA_metro)
# Top 5
IA_2000_t5=nm_IA_metro_dt[order(total_2000,decreasing = T)[1:5],][,c("name","total_2000")]
IA_2000_t5

IA_1990_t5=nm_IA_metro_dt[order(total_1990,decreasing = T)[1:5],][,c("name","total_1990")]
IA_1990_t5

IA_1980_t5=nm_IA_metro_dt[order(total_1980,decreasing = T)[1:5],][,c("name","total_1980")]
IA_1980_t5

#Last 5
nm_IA_metro_dt= nm_IA_metro_dt[,total_2000.abs:=abs(total_2000)]
nm_IA_metro_dt= nm_IA_metro_dt[,total_1990.abs:=abs(total_1990)]
nm_IA_metro_dt= nm_IA_metro_dt[,total_1980.abs:=abs(total_1980)]

IA_2000_b5=nm_IA_metro_dt[order(total_2000.abs)[1:5],][,c("name","total_2000.abs")]
IA_2000_b5

IA_1990_b5=nm_IA_metro_dt[order(total_1990.abs)[1:5],][,c("name","total_1990.abs")]
IA_1990_b5

IA_1980_b5=nm_IA_metro_dt[order(total_1980.abs)[1:5],][,c("name","total_1980.abs")]
IA_1980_b5
```

State Minnesota with high and low net migration rates
```{r}

nm_MN_metro<-nm_metro%>%
  filter(stname=="Minnesota")
nm_MN_metro_dt<-as.data.table(nm_MN_metro)
# Top 5
MN_2000_t5=nm_MN_metro_dt[order(total_2000,decreasing = T)[1:5],][,c("name","total_2000")]
MN_2000_t5

MN_1990_t5=nm_MN_metro_dt[order(total_1990,decreasing = T)[1:5],][,c("name","total_1990")]
MN_1990_t5

MN_1980_t5=nm_MN_metro_dt[order(total_1980,decreasing = T)[1:5],][,c("name","total_1980")]
MN_1980_t5

#Last 5
nm_MN_metro_dt= nm_MN_metro_dt[,total_2000.abs:=abs(total_2000)]
nm_MN_metro_dt= nm_MN_metro_dt[,total_1990.abs:=abs(total_1990)]
nm_MN_metro_dt= nm_MN_metro_dt[,total_1980.abs:=abs(total_1980)]

MN_2000_b5=nm_MN_metro_dt[order(total_2000.abs)[1:5],][,c("name","total_2000.abs")]
MN_2000_b5

MN_1990_b5=nm_MN_metro_dt[order(total_1990.abs)[1:5],][,c("name","total_1990.abs")]
MN_1990_b5

MN_1980_b5=nm_MN_metro_dt[order(total_1980.abs)[1:5],][,c("name","total_1980.abs")]
MN_1980_b5
```

State-IL: the counties with max and min net migration rate
```{r}
## Max

IL_max_2000 = nm_IL_metro_dt[total_2000==max(total_2000),.(total_2000, name)]
IL_max_2000 

IL_max_1990 = nm_IL_metro_dt[total_1990==max(total_1990),.(total_1990, name)]
IL_max_1990 

IL_max_1980 = nm_IL_metro_dt[total_1980==max(total_1980),.(total_1980, name)]
IL_max_1980 

##Min
nm_IL_metro_dt= nm_IL_metro_dt[,total_2000.abs:=abs(total_2000)]
nm_IL_metro_dt= nm_IL_metro_dt[,total_1990.abs:=abs(total_1990)]
nm_IL_metro_dt= nm_IL_metro_dt[,total_1980.abs:=abs(total_1980)]

IL_min_2000 = nm_IL_metro_dt[total_2000.abs==min(total_2000.abs),.(total_2000.abs, name)]
IL_min_2000 

IL_min_1990 = nm_IL_metro_dt[total_1990.abs==min(total_1990.abs),.(total_1990.abs, name)]

IL_min_1990 

IL_min_1980 = nm_IL_metro_dt[total_1980.abs==min(total_1980.abs),.(total_1980.abs, name)]
IL_min_1980 


```







State-ND: the counties with max and min net migration rate
```{r}
nm_ND_metro<-nm_metro%>%
  filter(stname=="North Dakota")
nm_ND_metro_dt<-as.data.table(nm_ND_metro)

## Max

ND_max_2000 = nm_ND_metro_dt[total_2000==max(total_2000),.(total_2000, name)]
ND_max_2000 

ND_max_1990 = nm_ND_metro_dt[total_1990==max(total_1990),.(total_1990, name)]
ND_max_1990 

ND_max_1980 = nm_ND_metro_dt[total_1980==max(total_1980),.(total_1980, name)]
ND_max_1980 

##Min
nm_ND_metro_dt= nm_ND_metro_dt[,total_2000.abs:=abs(total_2000)]
nm_ND_metro_dt= nm_ND_metro_dt[,total_1990.abs:=abs(total_1990)]
nm_ND_metro_dt= nm_ND_metro_dt[,total_1980.abs:=abs(total_1980)]

ND_min_2000 = nm_ND_metro_dt[total_2000.abs==min(total_2000.abs),.(total_2000.abs, name)]
ND_min_2000 

ND_min_1990 = nm_ND_metro_dt[total_1990.abs==min(total_1990.abs),.(total_1990.abs, name)]

ND_min_1990 

ND_min_1980 = nm_ND_metro_dt[total_1980.abs==min(total_1980.abs),.(total_1980.abs, name)]
ND_min_1980 


```
State-colorado: the counties with max and min net migration rate

```{r}

nm_CO_metro<-nm_metro%>%
  filter(stname=="Colorado")

nm_CO_metro_dt<-as.data.table(nm_CO_metro)

nm_CO_metro_dt=na.omit(nm_CO_metro_dt)
## Max

CO_max_2000 = nm_CO_metro_dt[total_2000==max(total_2000),.(total_2000, name)]
CO_max_2000 

CO_max_1990 = nm_CO_metro_dt[total_1990==max(total_1990),.(total_1990, name)]
CO_max_1990 

CO_max_1980 = nm_CO_metro_dt[total_1980==max(total_1980),.(total_1980, name)]
CO_max_1980 

##Min
nm_CO_metro_dt= nm_CO_metro_dt[,total_2000.abs:=abs(total_2000)]
nm_CO_metro_dt= nm_CO_metro_dt[,total_1990.abs:=abs(total_1990)]
nm_CO_metro_dt= nm_CO_metro_dt[,total_1980.abs:=abs(total_1980)]

CO_min_2000 = nm_CO_metro_dt[total_2000.abs==min(total_2000.abs),.(total_2000.abs, name)]
CO_min_2000 

CO_min_1990 = nm_CO_metro_dt[total_1990.abs==min(total_1990.abs),.(total_1990.abs, name)]

CO_min_1990 

CO_min_1980 = nm_CO_metro_dt[total_1980.abs==min(total_1980.abs),.(total_1980.abs, name)]
CO_min_1980 


```

